---
output:
  github_document:
    html_preview: false
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```


## Overview

`"binomial` is a package that provides functions helpful in computing binomials

- `bin_choose` computes choose n k
- `bin_distribution` build a table with # of success and probs.
- `bin_cumulatve` build a table on top of distribution a collumn for culmulative.
- `bin_probability` computes binomial probability.
- `bin_variable` useful for computng various statistics given binomials.


## Motivation

This package has been created for users who have to compute binomials but don't want to go thorugh hassles of making thier own custom functions.


## Installation

Install the development version from GitHub via the package `"devtools"`:

## Usage

```{r}
library(binomial)
# checkers
check_trials(5)
check_prob(0.5)
check_success(2, 2)
# auxiliaries
aux_kurtosis(5, 0.5)
aux_mean(5, 0.5)
aux_mode(5, 0.5)
aux_variance(5, 0.5)
aux_skewness(5, 0.5)
# binomials functions
bin_choose(5, 2)
bin_probability(2, 3, 0.5)
bin_distribution(5, 0.5)
bin_culmulative(5, 0.5)
bin_variable(5, 0.5)
```
