---
title: "introduction"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(binomial)
```

## Binomial

The package `binomial` helps you compute binomial probability without making your own binomial functions manually.


## Checkers

Checkers check if input is in right form:

```{r}
check_prob(0.5)
check_trials(5)
check_success(2, 5)
```


## Auxillarys

Auxillary functions compute basic figure such as mean, mode, variance etc given trials and prob

```{r}
aux_mean(5, 0.5)
aux_mode(5, 0.5)
aux_variance(5, 0.5)
aux_skewness(5, 0.5)
aux_kurtosis(5, 0.5)
```


## Binomials

Binomial functions compute binomial probability, distribution and even culmulative and will give you nice table or plot corresponding to given distribution.

```{r}
bin_choose(5, 2)
bin_probability(2, 5, 0.5)
bin_distribution(5, 0.5)
bin_culmulative(5, 0.5)
a <- bin_distribution(5, 0.5)
a
plot(a)
b <- bin_culmulative(5, 0.5)
b
plot(b)
bin_variable(5, 0.2)
c <- bin_variable(5, 0.2)
c
summary(c)
```
